---
title: "Programing Assignment 3"
author: "Joel Negron"
date: "12/20/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 Plot the 30-day mortality rates for heart attack

Read the outcome data into R via the read.csv function and look at the rst few rows.

```{r}
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
```

There are many columns in this dataset. You can see how many by typing ncol(outcome) (you can see
the number of rows with the nrow function). In addition, you can see the names of each column by typing
names(outcome) (the names are also in the PDF document.)

To make a simple histogram of the 30-day death rates from heart attack (column 11 in the outcome dataset),
run:
```{r, echo = FALSE, warning=FALSE}
outcome[, 11] <- as.numeric(outcome[, 11])
hist(outcome[, 11])

```
Because we originally read the data in as character (by specifying colClasses = "character" we need to
coerce the column to be numeric. You may get a warning about NAs being introduced but that is okay.

## 2 Finding the best hospital in a state

```{r, error=TRUE}
source('best.R')

best('TX', "heart attack")
best("TX", "heart failure")
best("MD", "heart attack")
best("MD", "pneumonia")
best("BB", "heart attack")
best("NY", "hert attack")
```

## 3 Ranking hospitals by outcome in a state

```{r, error=TRUE}
source('rankhospital.R')

rankhospital("TX", "heart failure", 4)
rankhospital("MD", "heart attack", "worst")
rankhospital("MN", "heart attack", 5000)
```

## 4 Ranking hospitals in all states

```{r, error=TRUE}
source('rankall.R')

head(rankall("heart attack", 20), 10)
tail(rankall("pneumonia", "worst"), 3)
tail(rankall("heart failure"), 10)
```

## Assignment Questions

```{r, error=TRUE}
source('rankhospital.R')
source('best.R')
source('rankall.R')

best("SC", "heart attack")
best("NY", "pneumonia")
best("AK", "pneumonia")
rankhospital("NC", "heart attack", "worst")
rankhospital("WA", "heart attack", 7)
rankhospital("TX", "pneumonia", 10)
rankhospital("NY", "heart attack", 7)

r <- rankall("heart attack", 4)
as.character(subset(r, state == "HI")$hospital)

r <- rankall("pneumonia", "worst")
as.character(subset(r, state == "NJ")$hospital)

r <- rankall("heart failure", 10)
as.character(subset(r, state == "NV")$hospital)
```